Artificial Neural Network based critical conditions for Dynamic Recrystallization of Medium Carbon Steel and Application

### 2023-08-24 Article.tex
Split paragraphs
Update abstract and title page

% Author Orchid ID: enter ID or remove command
\newcommand{\orcidauthorA}{0000-0001-7367-5453} % Add \orcidA{} behind the author's name
\newcommand{\orcidauthorB}{0000-0002-1522-2787} % Add \orcidB{} behind the author's name
\newcommand{\orcidauthorC}{0000-0002-5360-5121}% Add \orcidB{} behind the
%author's name
\newcommand{\orcidauthorD}{0000-0002-0815-1984}

@@

% Contact information of the corresponding author
\corres{Correspondence: Olivier.Pantale@enit.fr; Tel.: +33-562442933}

@@

% Abstract (Do not insert blank lines, i.e. \\)
\abstract{This study presents a novel and comprehensive approach for understanding and simulating the dynamic recrystallization (DRX) process during hot compression. To achieve this, the high-temperature deformation behavior of a medium carbon steel was studied over a wide range of strains, strain rates, and temperatures using hot compression tests on a Gleeble-3800 and ANN based flow behaviour law was used to model the plastic behaviour. The accuracy of the DRX volumic fraction, both during its identification using analytical models and its numerical implementation in finite element software, relies on critical conditions and therfore, in this study, an artificial neural network, as a universal approximator, is proposed to fit the necessary data for calculating the critical conditions of DRX. The JMAK model was used as an analytical model to calculate the volumic fraction of DRX, and its validation against experimental data was successful. A numerical implementation of the Johnson-Mehl-Avrami-Kohnogorov (JMAK) model was implemented into ABAQUS software, and the obtained results were compared with experimental data through microstructure analysis, revealing a strong correlation between simulation and experimentation. Temperature, strain rate and the amount of deformation effects on DRX evoultion were also investigated in this study and it was observed that the DRX rises with temperature and deformation while it decreases with the increase of strain rates.
}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Only for the journal Applied Sciences
%\featuredapplication{Authors are encouraged to provide a concise description of the specific application or a potential application of the work. This section is not mandatory.}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

The accuracy of the critical conditions for DRX is strongly related to how the curve $\theta=f(\sigma)$ is obtained. Indeed, the direct use of raw data from experiments does not provide usable curves. Therefore, commonly used methods involve either smoothing the curve $\sigma=f(\varepsilon)$  as much as possible or approximating this curve with a polynomial function that can reproduce it and deducing the curve $\theta=f(\sigma)$ from it. The disadvantage of these two methods is that they do not always guarantee a good smoothing of the curve $\sigma=f(\varepsilon)$. However, an Artifical Neural Networks (ANN) method is a universal approximator that has proven its effectiveness in several fields, including predicting the material's flow behavior. Based on this tool, we propose, in this study, to replace the two smoothing methods with an ANN to obtain the critical conditions for DRX. In other words, the proposed approach suggests using an ANN to model the relationship between the stress ($\sigma$) and the rate hardening ($\theta$) directly, avoiding the need for explicit smoothing of experimental data. By training the ANN with appropriate data, it can learn the underlying relationship between stress and DRX, thus providing a more accurate estimation of the critical conditions for DRX.

%----------------------------------------------------------------------------------
\section{Materials and experiments\label{sec:MaterialsExperiments}}
%----------------------------------------------------------------------------------
The experimental tests on which this work is based are strictly identical to those already published by Tize Mha \eal \cite{TizeMha-2023}.
For further information, readers may refer to this other publication by our research group. We will, however, list here-after the main points required to understand the proposed approach. The first publication focused on developing a constitutive law capable of predicting material flow, for which a comparative study between 5 analytical models and a neural network-based model was conducted. At the conclusion of this comparative study, the Artificial Neural Network (ANN) model proved to be the best performing. In this new study, the ANN model will be utilized for predicting dynamic recrystallization, as explained in the introduction. It's worth noting that the ANN model identified in the first publication will also be employed for managing the plastic behavior of the material.

>>>>

% Author Orchid ID: enter ID or remove command
\newcommand{\orcidauthorA}{0000-0001-7367-5453}
\newcommand{\orcidauthorB}{0000-0002-1522-2787}
\newcommand{\orcidauthorC}{0000-0002-5360-5121}
\newcommand{\orcidauthorD}{0000-0002-0815-1984}

@@

% Contact information of the corresponding author
\corres{Correspondence: olivier.pantale@enit.fr; Tel.: +33-562442933}

@@

% Abstract (Do not insert blank lines, i.e. \\)
\abstract{This study presents a novel and thorough approach to comprehending and simulating the DRX process while hot-compressing steel.
To achieve this goal, we studied the high-temperature deformation behavior of a medium-carbon steel through hot compression testing on a Gleeble-3800 thermomechanical simulator over a broad range of strains, strain rates, and temperatures.
We also employed an artificial neural network (ANN) to model thermo-visco-plastic behavior with a flow law.
The precision of quantifying DRX volume fraction is dependent on critical conditions, which are essential for both analytical model evaluation and numerical implementation in finite element software.
This study proposes a second ANN, serving as a universal approximator, to fit the data required for DRX critical condition calculations.
The Johnson-Mehl-Avrami-Kohnogorov (JMAK) model served as an analytical tool to estimate the DRX volume fraction, which underwent validation through experimental measurements.
A numerical implementation of the JMAK model was conducted in ABAQUS software and compared against experimental data by means of microstructure analysis.
The comparison revealed a strong correlation between simulation and experiment.
The study investigated the impact of temperature, deformation magnitude, and strain rate on DRX evolution.
The findings showed that DRX increases with rising temperature and strain, but decreases with increasing strain rate.}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Only for the journal Applied Sciences
%\featuredapplication{Authors are encouraged to provide a concise description of the specific application or a potential application of the work.This section is not mandatory.}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

The accuracy of the critical conditions for DRX is strongly related to how the curve $\theta=f(\sigma)$ is obtained.
Indeed, the direct use of raw data from experiments does not provide usable curves.
Therefore, commonly used methods involve either smoothing the curve $\sigma=f(\varepsilon)$  as much as possible or approximating this curve with a polynomial function that can reproduce it and deducing the curve $\theta=f(\sigma)$ from it.
The disadvantage of these two methods is that they do not always guarantee a good smoothing of the curve $\sigma=f(\varepsilon)$.
However, an Artifical Neural Networks (ANN) method is a universal approximator that has proven its effectiveness in several fields, including predicting the material's flow behavior.
Based on this tool, we propose, in this study, to replace the two smoothing methods with an ANN to obtain the critical conditions for DRX.
In other words, the proposed approach suggests using an ANN to model the relationship between the stress ($\sigma$) and the rate hardening ($\theta$) directly, avoiding the need for explicit smoothing of experimental data.
By training the ANN with appropriate data, it can learn the underlying relationship between stress and DRX, thus providing a more accurate estimation of the critical conditions for DRX.
%----------------------------------------------------------------------------------
\section{Materials and experiments\label{sec:MaterialsExperiments}}
%----------------------------------------------------------------------------------
The experimental tests on which this work is based are strictly identical to those already published by Tize Mha \eal \cite{TizeMha-2023}.
For further information, readers may refer to this other publication by our research group.
We will, however, list here-after the main points required to understand the proposed approach.
The first publication focused on developing a constitutive law capable of predicting material flow, for which a comparative study between 5 analytical models and a neural network-based model was conducted.
At the conclusion of this comparative study, the Artificial Neural Network (ANN) model proved to be the best performing.
In this new study, the ANN model will be utilized for predicting dynamic recrystallization, as explained in the introduction.
It's worth noting that the ANN model identified in the first publication will also be employed for managing the plastic behavior of the material.
